The thin blue line:\\what protects my Android device?

### 2015-03-31 securityupdates.tex
Minor fixes

\subsection{Analysis 1: vulnerability of Android devices}\label{sec:exp:versionsecurity}
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe secure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
}
\label{fig:proportioninsecure}
\end{figure}
In this analysis we calculate the proportion of Android devices which are exposed to critical vulnerabilities and and discuss how that has changed over time.
In Figure~\ref{fig:proportioninsecure} describes the proportion of Android devices susceptible to at least one critical vulnerability.

@@

The longitudinal data on the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to \da\ changes over time is shown in Figure~\ref{fig:device_data_security}.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, mostly not fixed.
This implies that these devices had been abandoned by the device manufacturer and were not receiving updates, this is confirmed by Figure~\ref{fig:device_data_os} which shows which OS versions those devices were running.
Some devices start off in 2011 exposed to known security vulnerabilities and are still exposed to those and additional ones in 2014.

>>>>

\subsection{Analysis 1: vulnerability of Android devices}\label{sec:exp:versionsecurity}
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe secure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
}
\label{fig:proportioninsecure}
\end{figure}
In this analysis we calculate the proportion of Android devices which are exposed to critical vulnerabilities and and discuss how that has changed over time.
Figure~\ref{fig:proportioninsecure} describes the proportion of Android devices susceptible to at least one critical vulnerability.

@@

The longitudinal data on the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to \da\ changes over time is shown in Figure~\ref{fig:device_data_security}.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and mostly not fixed.
This implies that these devices had been abandoned by the device manufacturer and were not receiving updates, this is confirmed by Figure~\ref{fig:device_data_os} which shows which OS versions those devices were running.
Some devices start off in 2011 exposed to known security vulnerabilities and are still exposed to those and additional ones in 2014.
